18.821 Project 2

### 2014-10-28 paper/paper.tex
made a few changes

Before, beginning our discussion, we present the following definitions.

@@

\begin{definition} 
When $n\ge k$, a permutation $\sigma\in S_n$ avoids a permutation $\pi\in S_k$ if $\pi$ and $\sigma$ avoid each other when written as sequences in one-line notation. 
\end{definition}

\begin{definition}
For a permutation $\pi$, $s_n(\pi)$ represents the number of permutations in $S_n$ that avoid $\pi$. 
\end{definition}

@@

\subsection{Flipping}
Another concept that we will use in this paper is the concept of flipping. We define the \emph{flip} of a sequence $a$ as the sequence $b$ with the same elements as $a$, but with elements in the opposite order. More concretely, if $a = a_1, a_2, \dots, a_n$ for some arbitrary $n$, then the flip of the sequence $a$ will be the sequence $b = a_n, a_{n-1}, \dots, a_2, a_1$.

>>>>

Before beginning our discussion, we present the following definitions.

@@

\begin{definition} 
A permutation $\sigma\in S_n$ avoids a permutation $\pi\in S_k$ if the sequence of numbers for the one-line notation for $\sigma$ avoids the sequence of numbers for the one-line notation for $\pi$.
\end{definition}

\begin{definition}
For a permutation $\pi\in S_k$, $s_n(\pi)$ represents the number of permutations in $S_n$ that avoid $\pi$. 
\end{definition}

@@

\subsection{Flipping}
Another notion that we will use in this paper is the concept of flipping. We define the \emph{flip} of a sequence $a$ as the sequence $b$ with the same elements as $a$, but with elements in the opposite order. More concretely, if $a = a_1, a_2, \dots, a_n$ for some arbitrary $n$, then the flip of the sequence $a$ will be the sequence $b = a_n, a_{n-1}, \dots, a_2, a_1$.
